Wavefield Reconstruction Inversion: an example

### 2020-08-01 repro/papers/wri1d/rev1/response.tex

\address{email: {\tt symes@rice.edu}}
\title{Responses to reviews of ``Wavefield Reconstruction Inversion: an example'', submitted to Inverse Problems}
\author{William. W. Symes}

\lefthead{Symes}

\righthead{1D WRI}

\section{Responses to Referee Comments}
I very much appreciate the careful and constructive criticisms provided by the referees, and have attempted to address every point they have made, at the cost of lengthening the paper somewhat.

\section{Referee 1}

\noindent Comment: (1)The theory is credible, however, I also suggest that you’d better supply some numerical examples;

\noindent Response: I have added a short section with a numerical example.

\noindent Comment: (2)In the section of abstract, I suggest that you should focus on our new method;

\noindent Response: Indeed, I would love to do so, but you have the advantage of me: I don't know who you are, and even more don't know what your ``new method'' is. Also note that abstracts should not include references.

\noindent Comment: (3)Equations (1),(4)-(7), (9), (12)-(14), (19), (21), (23)-(26), (28)-(32): lack of punctuation marks;

\noindent Response: thank you - I have attempted to properly punctuate every equation, and appreciate you calling these out.

\noindent Comment: (4)Pg. 2, line 12: “((Bamberger et al.,” Please delete a “(”.

\noindent Response: thank you for pointing this out.

\noindent Comment: (5)DISCUSSION: operator-valiued-->operator-valued;

\noindent Response: Fixed, thanks.

\noindent Comment: (6)In the section of Introduction, please supply the researches in the last three years.

\noindent Response: I have added more references, to make clear tha work on WRI continues right up to the present. This paper is not meant to be a review of WRI - that is for someone more involved in it to write. I just want to make the point that the claims offered for WRI as a cycle-skip remedy are clearly wrong, by showing a counter-example to which these claims should also apply.

\section{Referee 2}

\noindent Comment: on the relation between WRI and MSWI.

\noindent Response: You have made me aware that my first draft was too glib about the relation between these various approaches. I have added a full description of the relation between ``traditional'' WRI as formulated by van Leeuwen and Herrmann, and the variant of MSWI that I call WRI in this paper. In fact they are completely equivalent under conditions that hold for the problem I consider, in that (1) the original formulation of the vL-H GJI 2013 paper and the VPM reduction as in their 2016 IP paper have stationary points and local minima in 1-1 correspondence, and (2) the VPM-WRI of the 2016 IP paper and the VPM reduction of the problem stated in display 2 of my paper also have stationary points and local minima in 1-1 correspondence - it could not be otherwise, as these two reduced objectives are the same function! The equivalence (1) is a consequence of the separable part of the objective (that is, the dependence on the state variable) being strictly convex quadratic. In any case, while this discussion bulks up the paper a bit, I agree that it is really necessary to fully support my conclusions - namely, it would not matter what version of WRI you use, you will wind up with the same behaviour.

I also gave a more detailed (but still rough) account of the theoretical results of van Leeuwen and Herrmann from their 2016 IP paper, and tried to identify clearly the reason advanced in most papers on the topic to think WRI might overcome cycle-skipping - namely bigger search space, that is, merely the fact that it uses extended modeling. Further, I pointed out that the theory developed in my paper applies precisely to the 1D transmission problem, and not to any other WRI implementation (necessarily). However the arguments in favor of WRI also apply, and therefore are shown to be (at least) incomplete.

\noindent Comment: on other approaches to convexifying FWI.

\noindent Response: I have added a few sentences in the introduction, with some recent references, on the use of the Wasserstein metric. Also, I identified WRI as being based on extended modeling, and gave a reference which includes a discussion of MVA and related ideas (and some historical stuff, as extended modeling is really an old story). You are right that these things should be mentioned, and of course more could be said, eg. about tomography, but I hesitate to do muich more than this, as the paper begins already to become a bit top-heavy.

\noindent Detailed Comments:

\noindent Response: many thanks! I believe I have addressed them all.

\noindent [Except for the first: ``...requires that the intial estimate predict...'' is a weird bit of English grammar called a modal verb phrase - ``requires that'' is the modal verb (a compound, unlike ``must'' or ``should'') and ``predict'' is the auxiliary verb, which is always used in its base (infinitive) form. So no ``s''. Another example: ``he must dig a hole'' vs. ``he digs a hole''. This is really obscure, sorry, there is nothing more confusing than English grammar.]

### 2020-08-01 repro/papers/wri1d/rev1/paper.tex
rev1 and submission versions

\title{Wavefield Reconstruction Inversion: an example}
\author{William. W. Symes \thanks{The Rice Inversion Project,
Department of Computational and Applied Mathematics, Rice University,
Houston TX 77251-1892 USA, email {\tt symes@caam.rice.edu}.}}

@@

\begin{abstract}
  Full waveform inversion, or nonlinear least squares data-fitting
  driven by wave equation simulation, has proven its ability to
  extract detailed maps of earth structure from near-surface seismic
  observations. However, the least squares error function at the heart
  of this method tends to develop a high degree of nonconvexity, so
  that local optimization methods (the only numerical methods feasible
  for field-scale problems) tend to fail, unless provided with initial
  estimates of a quality not always available. A number of alternative
  optimization principles have been advanced that promise some degree
  of release from the multimodality of Full Waveform Inversion,
  amongst them Wavefield Reconstruction Inversion, the focus of this
  paper. Applied to a simple 1D acoustic transmission problem, both
  Full Waveform and Wavefield Reconstruction Inversion methods reduce
  to minimization of explicitly computable functions, in an asymptotic
  sense. The analysis presented here shows that Wavefield
  Reconstruction Inversion can be vulnerable to the same
  ``cycle-skipping'' failure mode as Full Waveform Inversion.
\end{abstract}

@@

Full waveform inversion (FWI) is the current nomenclature in the
seismology literature for data-fitting earth structure estimation
driven by wavefield modeling. The earth properties to be estimated
(material densities, stiffnesses, attenuation rates,...) form a vector
$c$ of spatially fields that appear as coefficients in systems of hyperbolic
partial differential equations, modeling seismic wave
propagation. The wavefields used in structure estimation (``imaging'')
are small motion disturbances of the earth's equilibrium state, so the
equations of motion are typically 
linear(ized). Right-hand side vectors $f$ in these systems model energy
input that initiates waves (earthquakes, man-made sources such as
explosives or mechanical vibrators). Data vectors $d$ are simulated by
sampling the solution fields at the locations of measurement devices
(accelerometers, microphones,...)  over appropriate time
intervals. The relation between the energy source $f$ and the
simulated data is linear in $f$, but nonlinear in the coefficient
vector $c$, so is naturally represented by a family of linear
operators $S[c]$ parametrized by the coefficient vector $c$.

The objective of FWI is to find $c$ and $f$, given $d$, so that
$S[c]f \approx d$. A typical method for enforcing this requirement is
the minimization of an objective misfit measure (objective, for
short), the most common choice being the square norm of a Hilbert
space in which the data is presumed to reside:
\begin{equation}
  \label{eqn:deffwi}
  \mbox{Given } d, \mbox{ find }c \mbox{ and }f \mbox{ to
    minimize }
  \|d -  S[c]f\|^2
\end{equation}
in which $\|\cdot\|$ is the norm in a suitable Hilbert space. This
approach was first suggested in the 1980's
(\cite[]{BamChavLai:79,Tara:84a,KolbColLai:86,Crasetal:90}, and many
other papers since then). Usually some form of regularization is
applied, to compensate for poorly determined aspects of $c$ and/or
$f$, as is explained in Tarantola's influential book
\cite[]{Tarantola:05}. Also, $f$ may be constrained in one way or
another to embody characteristics of field energy sources, or even
regarded as known (an example of this is given below).

Within a few years of its introduction into quantitative seismology,
FWI was understood to suffer from a severe limitation. Because of the
typical dimensions of earth models, and consequent cost of accurate
computation of $S$, iterative local optimization provides the only
feasible route to estimation of $c$ via solution of the optimization
problem \ref{eqn:deffwi}. However the objective function of this
optimization problem (the mean-square residual appearing in display \ref{eqn:deffwi}) has many local minima in general, most
having nothing to do with a usable estimate of earth structure. [An
explicit example of this multi-modal behaviour appears below.]
Reliable estimation of $c$ via iterative local optimization requires
that the initial estimate predict the correct arrival time of waves,
as they appears in the data, within a wavelength at dominant
frequencies \cite[]{GauTarVir:86,VirieuxOperto:09}.

Despite this severe constraint, FWI has shown enough promise as a tool
for both industrial and academic seismology that it is now a
mainstream research topic, and to some extent a commercial
product. Estimation of sufficiently accurate initial models via
non-FWI methods is common practice, though what ``sufficiently
accurate'' means may be difficult to discern
\cite[]{Plessix:10}. The wavelength criterion mentioned in the last
paragraph may be made less onerous by collection of relatively
low-frequency data \cite[]{Wolfspar:16}. Finally, many alternatives to
straightforward least-squares data fitting have been suggested, some
of which appear to exhibit less tendency to develop local minima than
does the problem described in \ref{eqn:deffwi} \cite[]{Symes:09}.

This topic of this paper is one of these alternative approaches,
Wavefield Reconstruction Inversion (``WRI''). WRI was introduced by \cite{LeeuwenHerrmannWRI:13}, and further
developed by \cite{LeeuwenHerrmann:16,WangYingst:SEG16} and other
authors. It is based on the presumption that the correct source (right
hand side in the equations of motion) $q$ is
known, and combines a penalty for data misfit with a penalty for
failing to solve the equations of motion with the correct right hand side:
\begin{equation}
  \label{eqn:defwri}
  \mbox{Given } d \mbox{ and }q, \mbox{ find }c \mbox{ and }f \mbox{ to
    minimize }
  \|d -  S[c]f\|^2+\alpha^2\|f-q\|^2.
\end{equation}
Examples given
by \cite{LeeuwenHerrmannWRI:13} and others suggest that the problem
defined in display \ref{eqn:defwri} is less likely to develop
uninformative local minima if $\alpha$ is small. This might be so for
several reasons: one is that when less weight is
put on making the residual in the wave equation ($f-q$) small, 
$f$ may be chosen to make the data residual $d-S[c]f$ small
instead. One aspect of failure to predict the arrival times of waves
accurately is that small data residual is then difficult to
achieve. By maintaining fidelity to
the data, local minimization of the WRI objective might provide a
spurious-minimum-free path to a satisfactory estimate of $c$.

The main result of this paper is that in one simple case, in which all
of the necessary computations can be carried out by hand, this hope is
not realized: minimization of the WRI objective is just as likely to
be trapped in a spurious local minimizer as is the FWI objective.  The
context of this conclusion is a simple transmission inverse problem
for the 1D acoustic wave system, which models pulse transmission along
a 1D continuum from a source point to a receiver point. The pulses
used in this thought experiment are short, so the main information
content of the data is the time of transit from source to
receiver. The predominant information about the material model, in
this case reduced to the wave velocity (a scalar function of
position), is just this transit time, so I constrain both the target
wave velocity $c_*$ generating the data and the trial wave velocity
$c$ to be constant, that is, independent of position along the 1D
continuum. I introduce a family of inverse problems, depending on a
parameter $\lambda$ playing the role of wavelength. For sufficiently small
$\lambda$, it is possible to show explicitly that the FWI problem
possesses local minimizers far from the global minimizer at the target
$c_*$, and that initiating a local iterative optimization, such as
steepest descent or Newton's method, at a distance from $c_*$ bounded
below by a multiple of the ``wavelength'' $\lambda$ will result in
convergence to these spurious local minima. That is, FWI 
behaves in exactly the manner described in much of the literature on
this topic. However, an analysis of WRI applied to the same context
yields the same result: spurious local minima exist for sufficiently
small $\lambda$, and will be found by local optimization unless the
starting point is within $O(\lambda)$ of the target. That is, WRI
behaves in a manner qualitatively indistinguishable from FWI. In
particular, its ability to allow good fit to data for small $\alpha$
does not safeguard it from failure to converge globally to a ``good''
local minimum. In fact, the $\alpha \rightarrow 0$ limit of the WRI
objective is well-defined (after scaling by $1/\alpha^2$) and also behaves in
qualitatively the same way as the FWI objective. So the apparent
ability to maintain better data fit via reduction of $\alpha$ does not
lead to global behaviour asymptotically more amenable to local optimization.

This paper begins with a description of the 1D inverse transmission
problem and explicit computation of various components of the FWI
approach, based on explicit solution of the 1D acoustic system
presented in Appendix A. In the third section I introduce the $\lambda-$dependent
family of problems, and establish the asymptotic properties of FWI as
$\lambda \rightarrow 0$. The fourth section develops the algebraic
structure of WRI, culminating in a remarkable identity revealing WRI
to be equivalent to minimization of a weighted norm of the data
residual, with a weight operator depending on the coefficient vector
$c$. This identity has also been derived by \cite{Leeuwen2019note},
using a different argument. The result is quite general, applying to essentially any
realization of WRI, and already shows that its behaviour must be
closely related to that of FWI. In the fifth section I return to 
1D acoustics problem and the $\lambda$-dependent family of inverse
problems, compute that weight operator explicitly, and deduce the
global behaviour of WRI in this instance. The paper ends with a
discussion of the relation of the analysis presented here to a
previous analysis of optimization formulations of wave inversion
problems based on parameter-dependent quadratic forms
\cite[]{StolkSymes:03}, and a brief discussion of some other
alternatives to FWI.

\section{FWI for 1D Acoustics}
The example of FWI to be explored in this paper is one of the simplest possible, based on the 1D acoustics system connecting excess pressure $p$, particle velocity $v$, sonstitutive law defect (``source'') $f$, density $\rho$, and wave velocity $c$:
\begin{eqnarray}
\label{eqn:awe1d}
\frac{\partial p}{\partial t} + \rho c^2\frac{\partial 
  v}{\partial z} &=& f \nonumber\\
\rho \frac{\partial v}{\partial t} + \frac{\partial p}{\partial 
  z}&=&0\nonumber\\
 p,v&=&0, t \ll 0. 
\end{eqnarray}
The fields $p,v,f$ are functions of spatial position $z \in \bR$ and time $t \in \bR$, whereas $c, \rho$ are functions of $z$ alone, so that the system \ref{eqn:awe1d} is autonomous.

@@

Limit observations to the time interval $[0,T]$, at the spatial (``receiver'')  location $z_r$. The modeling operator outputs the pressure trace $p(z_r,t)$ over the time interval $[0,T]$:
\begin{equation}
  \label{eqn:defmod}
  S[c]f = p|_{\{z_r\}\times [0,T]}
\end{equation}

The formulation of the inverse problem via least-squares requires a choice of Hilbert space structure for the domain and range of $S[c]$. A natural choice is
\begin{equation}
  \label{eqn:defmoddom}
  S[c]: L^2([z_{\rm min},z_{\rm max}] \times \bR) \rightarrow L^2[0,T]
\end{equation}
That is, the support of f will be assumed to lie in the strip $[z_{\rm min},z_{\rm max}] \times \bR$.
As it will turn out, the choice of spatial interval $[z_{\rm min},z_{\rm max}]$ is arbitrary, so long as it has positive length.

For homogeneous ($z$-independent) $\kappa$, Appendix A provides an explicit expression:
\begin{equation}
  \label{eqn:defmodhom}
  S[c]f(t) = \frac{1}{2c}\int_{z_{\rm min}}^{z_{\rm max}} dz f\left(z,t - \frac{|z_r-z|}{c}\right) 
\end{equation}
From this expression it is simple to see that $S[c]$ is a bounded
operator with the domain and range described in
\ref{eqn:defmoddom}. The role of compact support in $z$ in ensuring
boundedness is also evident.
%It is also evident from that limiting source to have bounded support in $z$ is necessary make $S[c]$ bounded.

With this framework, the data is presumed to lie in the range space of
$S[c]$: $d \in L^2[0,T]$. It is simple to verify from the identity
\ref{eqn:defmodhom} that $S[c]$ is also surjective. That is, any data
at all can be fit by $S[c]$ with an appropriate choice of input. This
observation is important in the development of WRI, to be explained
below.

@@

This point source field depends on a function of time (``wavelet'')
$w \in L^2(\bR)$. Formally, the resulting acoustic field satisfies the
system \ref{eqn:awe1d} with $f=w(t)\delta(z-z_s)$. Inserting this
expression in the explicit expression \ref{eqn:defmodhom}, obtain
\begin{equation}
  \label{eqn:defmodpt}
  S[c](w\delta(\cdot-z_s)) = \frac{1}{2c}w\left(t - \frac{|z_r-z_s|}{c}\right) = S_p[c]w(t)
\end{equation}
Thus for this restricted class of source fields, the FWI objective can be redefined as
\begin{equation}
  \label{eqn:deffwipt}
  J_{\rm FWI}[c,d.w] = \frac{1}{2}\|S_p[c]w -d\|^2.
\end{equation}
$S_p[c]$ is a bounded operator with domain $L^2(\bR)$ and range $L^2([0,T])$.

To end this section, it is necessary to address an irritating
technical point: the point source defined above is not a member of the
domain of $S[c]$, as it was defined in display \ref{eqn:defmoddom}, so
the left-hand side of equation \ref{eqn:defmodpt} does not actually
make sense. The fix for this incompatibility actually elucidates the
relation between $S[c]$ and $S_p[c]$. Appendix B describes the
construction of a family of bounded injective operators  $E[c]: L^2(\bR) \rightarrow L^2([z_{\rm min},z_{\rm max}] \times \bR)$ for which
\begin{equation}
  \label{eqn:ext}
  S_p[c] = S[c] \circ E[c]
\end{equation}
This relation exhibits $S[c]$ as an {\em extension} of $S_p[c]$ as
described by \cite{Symes:09}. WRI for 1D acoustic transmission is
based on $S[c]$, and so is identified as an extended version of FWI.

@@

>>>>

\address{email: {\tt symes@rice.edu}}
\title{Wavefield Reconstruction Inversion: an example}
\author{William. W. Symes\\Rice University}

@@

\begin{abstract}
  Nonlinear least squares data-fitting driven by physical process
  simulation is a classic and widely successful technique for the
  solution of inverse problems in science and engineering. Known as
  ``Full Waveform Inversion'' in application to seismology, it can
  extract detailed maps of earth structure from near-surface seismic
  observations, but also suffers from a defect not always encountered
  in other applications: the least squares error function at the heart
  of this method tends to develop a high degree of nonconvexity, so
  that local optimization methods (the only numerical methods feasible
  for field-scale problems) may fail to produce geophysically useful
  final estimates of earth structure, unless provided with initial
  estimates of a quality not always available. A number of alternative
  optimization principles have been advanced that promise some degree
  of release from the multimodality of Full Waveform Inversion,
  amongst them Wavefield Reconstruction Inversion, the focus of this
  paper. Applied to a simple 1D acoustic transmission problem, both
  Full Waveform and Wavefield Reconstruction Inversion methods reduce
  to minimization of explicitly computable functions, in an asymptotic
  sense. The analysis presented here shows explicitly how multiple
  local minima arise in Full Waveform Inversion, and that Wavefield
  Reconstruction Inversion can be vulnerable to the same
  ``cycle-skipping'' failure mode.
\end{abstract}

@@

Full waveform inversion (FWI) is the current nomenclature in the
seismology literature for data-fitting earth structure estimation
driven by wavefield modeling. The earth properties to be estimated
(material densities, stiffnesses, attenuation rates,...) form a vector
$c$ of spatially varying fields that appear as coefficients in systems of hyperbolic
partial differential equations, modeling seismic wave
propagation. The wavefields used in structure estimation (``imaging'')
are small motion disturbances of the earth's equilibrium state, so the
equations of motion are typically 
linear(ized). Right-hand side vectors $f$ in these systems model energy
input that initiates waves (earthquakes, man-made sources such as
explosives or mechanical vibrators). Data vectors $d$ are simulated by
sampling the solution fields at the locations of measurement devices
(accelerometers, microphones,...)  over appropriate time
intervals. The relation between the energy source $f$ and the
simulated data is linear in $f$, but nonlinear in the coefficient
vector $c$, so is naturally represented by a family of linear
operators $S[c]$ parametrized by the coefficient vector $c$.

The objective of FWI is to find $c$ and $f$, given $d$, so that
$S[c]f \approx d$. A typical method for achieving this goal is
the minimization of an objective misfit measure (objective, for
short), the most common choice being the square norm of a Hilbert
space in which the data is presumed to reside:
\begin{equation}
  \label{eqn:deffwi}
  \mbox{Given } d, \mbox{ find }c \mbox{ and }f \mbox{ to
    minimize }
  \|d -  S[c]f\|^2.
\end{equation}
In equation \ref{eqn:deffwi}, $\|\cdot\|$ is the norm in a suitable
Hilbert space.

This approach was first suggested in the 1980's
(\cite{BamChavLai:79,Tara:84a,KolbColLai:86,Crasetal:90}, and many
other papers since then). Usually some form of regularization is
applied, to compensate for poorly determined aspects of $c$ and/or
$f$, as is explained in Tarantola's influential book
\cite[]{Tarantola:05}. Also, $f$ may be constrained in one way or
another to embody characteristics of field energy sources, or even
regarded as known (an example of this is given below).

Within a few years of its introduction into quantitative seismology,
FWI was understood to suffer from a severe limitation. Because of the
typical dimensions of earth models, and consequent cost of accurate
computation of $S$, iterative local optimization provides the only
feasible route to estimation of $c$ via solution of the optimization
problem \ref{eqn:deffwi}. However the objective function of this
optimization problem (the mean-square residual appearing in display \ref{eqn:deffwi}) has many local minima in general, most
having nothing to do with a usable estimate of earth structure. [An
explicit example of this multi-modal behaviour appears below.]
Reliable estimation of $c$ via iterative local optimization requires
that the initial estimate predict the correct arrival time of waves,
as they appears in the data, within a wavelength (in fact,
conventionally a half wavelength) at dominant
frequencies \cite[]{GauTarVir:86,VirieuxOperto:09}.

Despite this severe constraint, FWI has shown enough promise as a tool
for both industrial and academic seismology that it is now a
mainstream research topic, and to some extent a commercial
product. Estimation of sufficiently accurate initial models via
non-FWI methods is common practice, though what ``sufficiently
accurate'' means may be difficult to discern
\cite[]{Plessix:10}. The wavelength criterion mentioned in the last
paragraph may be made less onerous by collection of relatively
low-frequency data \cite[]{Wolfspar:16}. Finally, many alternatives to
straightforward least-squares data fitting have been suggested, some
of which appear to exhibit less tendency to develop local minima than
does the problem described in \ref{eqn:deffwi}. For example, other
metrics than the $L^2$ distance employed in definition
\ref{eqn:deffwi} may be used to characterize the size
of the data residual $S[c]f-d$, and some of these result in larger
regions of convexity about global minima than possessed by the $L^2$ based
objective \ref{eqn:deffwi} . A particularly promising class of
alternative distance measures derives from optimal transport theory
\cite[]{EngquistYang:GEO18,Metivier:GEO18}. Of course, practical
seismology has estimated earth mechanical parameters, including wave
velocities, for decades. Some of these practical methods are based on
model extension, that is, the addition of extra degrees of freedom
beyond those required by basic physics. More recently, the extension
concept has been used to reformulate the FWI
problem. \cite{geoprosp:2008} describes several variants of
extension-based inversion and its origins in seismic data processing.

This topic of this paper is one of these extension-based inversion approaches,
Wavefield Reconstruction Inversion (``WRI''). WRI was introduced by \cite{LeeuwenHerrmannWRI:13}, and further
developed by \cite{LeeuwenHerrmann:16,WangYingst:SEG16,Lietal:18, Leeuwen2019note,Herrmann:SEG19,Aghamiry:19,FangWangHerrmann:20,Aghmiryetal:20,Louboutinetal:20}; and other
authors. It is based on the presumption that the correct source (right
hand side in the equations of motion) $q$ is
known, and combines a penalty for data misfit with a penalty for
failing to solve the equations of motion with the correct right hand side:
\begin{equation}
  \label{eqn:defwri}
  \mbox{Given } d \mbox{ and }q, \mbox{ find }c \mbox{ and }f \mbox{ to
    minimize }
  \|d -  S[c]f\|^2+\alpha^2\|f-q\|^2.
\end{equation}
The formulation of WRI given by \cite{LeeuwenHerrmannWRI:13}
appears to differ from the alternative formulation \ref{eqn:defwri},
introduced by \cite{WangYingst:SEG16} but in fact the two are
completely equivalent, in the sense of having corresponding local
minimizers. The original form and its equivalence with the problem
\ref{eqn:defwri} are explained in the fourth section of this paper. As
noted by \cite{Leeuwen2019note}, either formulation is available not
just for seismic inverse problems, but for any inverse problem based
on a separable (partly linear) modeling operator.

Numerical examples provided in the cited literature on WRI suggest
that the problem defined in display \ref{eqn:defwri} is less likely to
develop uninformative local minima (that is, is ``less nonlinear'') than
is the least squares problem \ref{eqn:deffwi} in application to
seismic inversion. The most-often cited justification for this point
of view is that the WRI problem \ref{eqn:defwri} involves a search for an
optimum over many more degrees of freedom than does the FWI problem
\ref{eqn:deffwi}, since the trial source $f$ is also to be
determined. More concretely, \cite{LeeuwenHerrmann:16} show that if
$(c_*,f_*)$ is a
stationary point of the objective defined in problem
\ref{eqn:defwri}, then $c_*$ is within (roughly) the data residual scaled by the
reciprocal penalty parameter (that is, $O(\alpha^{-1}\|d-S[c_*]f_*\|)$) of a
global FWI minimizer. [The precise statement
of this result, which follows from Theorem 4.3 in
\cite[]{LeeuwenHerrmann:16}, depends on analysis of the FWI problem
\ref{eqn:deffwi} as an equality-constrained optimization; we refer the
reader to the cited reference for details.] This is however a {\em
  local} characterization of WRI stationary points: it shows that
these are close to solutions of the FWI problem only
for those that produce a small data residual, and does not address the {\em
  global} question of whether large-residual stationary points exist,
as appears to be the case for FWI.
% , if $\alpha$ is sufficiently small. 
%This might be so for several reasons: one is that
%when less weight is put on making the residual in the wave equation
%($f-q$) small, $f$ may be chosen to make the data residual $d-S[c]f$
%small instead. One aspect of failure to predict the arrival times of
%waves accurately is that small data residual is then difficult to
%achieve. By maintaining fidelity to the data, local minimization of
%the WRI objective might provide a spurious-minimum-free path to a
%satisfactory estimate of $c$.

The main result of this paper is that in one simple case, in which all
of the necessary computations can be carried out by hand, the WRI
objective does indeed possess stationary points with large data residual.
% this hope is not realized:
In fact, in this case, minimization of the WRI objective is just as likely to
be trapped in a spurious local minimizer as is the FWI objective.  The
context of this conclusion is a simple transmission inverse problem
for the 1D acoustic wave system, which models pulse transmission along
a 1D continuum from a source point to a receiver point. The pulses
used in this thought experiment are short, so the main information
content of the data is the time of transit from source to
receiver. The predominant information about the material model, in
this case reduced to the wave velocity (a scalar function of
position), is just this transit time, so I constrain both the target
wave velocity $c_*$ generating the data and the trial wave velocity
$c$ to be constant, that is, independent of position along the 1D
continuum. I introduce a family of inverse problems, depending on a
parameter $\lambda$ playing the role of wavelength. For sufficiently small
$\lambda$, it is possible to show explicitly that the FWI problem
possesses local minimizers far from the global minimizer at the target
$c_*$, and that initiating a local iterative optimization, such as
steepest descent or Newton's method, at a distance from $c_*$ bounded
below by a multiple of the ``wavelength'' $\lambda$ will result in
convergence to these spurious local minima. That is, FWI 
behaves in exactly the manner described in much of the literature on
this topic. However, an analysis of WRI applied to the same context
yields the same result: spurious local minima exist for sufficiently
small $\lambda$, and will be found by local optimization unless the
starting point is within $O(\lambda)$ of the target. That is, WRI
behaves in a manner qualitatively indistinguishable from FWI. In
particular, its ability to allow good fit to data for small $\alpha$
does not safeguard it from failure to converge globally to a ``good''
local minimum. In fact, the $\alpha \rightarrow 0$ limit of the WRI
objective is well-defined (after scaling by $1/\alpha^2$) and also behaves in
qualitatively the same way as the FWI objective. So the apparent
ability to maintain better data fit via reduction of $\alpha$ does not
lead to global behaviour asymptotically more amenable to local
optimization.

I emphasize that this conclusion holds {\em a priori} for the 1D
transmission inverse problem described in the next section, and {\em
  only} for this problem. The results presented here imply nothing
about the behaviour of any other instance of WRI. In particular, the
analysis takes advantage of the diagonal (in fact, scalar) nature of
the operator $S[c]S[c]^T$ (the central role played by this operator
will become clear in the fourth section below). For other
problems, for instance the simple example presented in
\cite{Leeuwen2019note}, this operator is not diagonal, so the the
short cuts used in the analysis given here are not available. However,
it should be understood that the various heuristic justifications
found in the literature for expecting WRI to avoid cycle-skipping, and
the theoretical analysis in \cite{LeeuwenHerrmann:16}, all apply to
the 1D transmission problem as well, and therefore in themselves are
insufficient to imply avoidance of cycle-skipping.

This paper begins with a description of the 1D inverse transmission
problem and explicit computation of various components of the FWI
approach, based on explicit solution of the 1D acoustic system
presented in Appendix A. In the third section I introduce the
$\lambda-$dependent family of problems, and establish the asymptotic
properties of FWI as $\lambda \rightarrow 0$. The fourth section
develops the algebraic structure of WRI, culminating in a remarkable
identity revealing WRI to be equivalent to minimization of a weighted
norm of the data residual, with a weight operator depending on the
coefficient vector $c$. This identity has also been derived by
\cite{Leeuwen2019note}, using a different argument. The result is
quite general, applying to essentially any realization of WRI, and
already shows that its behaviour must be closely related to that of
FWI. In the fifth section I return to 1D acoustics problem and the
$\lambda$-dependent family of inverse problems, compute that weight
operator explicitly, and deduce the global behaviour of WRI in this
instance. This behaviour is illustrated by a very simple numerical
example in the sixth section. The paper ends with a discussion of the
relation of the analysis presented here to a previous analysis of
optimization formulations of wave inversion problems based on
parameter-dependent quadratic forms \cite[]{StolkSymes:03}, and a
brief discussion of an extension-based inversion approach using a different
penalty than does WRI, which in application to the 1D transmission
problem provably avoids cycle-skipping.

\section{FWI for 1D Acoustics}
The example of FWI to be explored in this paper is one of the simplest possible, based on the 1D acoustics system connecting excess pressure $p$, particle velocity $v$, constitutive law defect (``source'') $f$, density $\rho$, and wave velocity $c$:
\begin{eqnarray}
\label{eqn:awe1d}
\frac{\partial p}{\partial t} + \rho c^2\frac{\partial 
  v}{\partial z} &=& f \nonumber\\
\rho \frac{\partial v}{\partial t} + \frac{\partial p}{\partial 
  z}&=&0\nonumber\\
 p,v&=&0, t \ll 0. 
\end{eqnarray}
The fields $p,v,f$ are functions of spatial position $z \in \bR$ and time $t \in \bR$, whereas $c, \rho$ are functions of $z$ alone, so that the system \ref{eqn:awe1d} is autonomous.

@@

Limit observations to the time interval $[0,T]$, at the spatial (``receiver'')  location $z_r$. The modeling operator outputs the pressure trace $p(z_r,t)$ over the time interval $[0,T]$:
\begin{equation}
  \label{eqn:defmod}
  S[c]f = p|_{\{z_r\}\times [0,T]}.
\end{equation}
This trace is well-defined if $f$ is smooth, since then the solution
$(p,v)$ is smooth.
For homogeneous ($z$-independent) $c$, Appendix A provides an explicit expression:
\begin{equation}
  \label{eqn:defmodhom}
  S[c]f(t) = \frac{1}{2c}\int_{z_{\rm min}}^{z_{\rm max}} dz f\left(z,t - \frac{|z_r-z|}{c}\right). 
\end{equation}
From this expression it clear that $S[c]$ extends a bounded
operator
\begin{equation}
  \label{eqn:defmoddom}
  S[c]: L^2([z_{\rm min},z_{\rm max}] \times \bR) \rightarrow L^2[0,T].
\end{equation}
That is, the support of f will be assumed to lie in the strip $[z_{\rm
  min},z_{\rm max}] \times \bR$.  The choice of spatial interval
$[z_{\rm min},z_{\rm max}]$ is arbitrary, so long as it has positive
length. The role of compact support in $z$ in ensuring
boundedness of $S[c]$ is also evident from equation \ref{eqn:defmodhom}.

It should be mentioned that the triviality of the conclusion
\ref{eqn:defmoddom} is a happy accident of one space dimension: for
analogous hyperbolic initial-boundary value problems in more than one
space dimension, simple integral representations such as
\ref{eqn:defmodhom} are not to be expected, and the regularity of
traces becomes a much more involved matter - see for example
\cite{Symes:83}, \cite{Lasi:87}, and \cite{BaoSy:91b}.

The formulation of the inverse problem via least-squares requires a
choice of Hilbert space structure for the domain and range of $S[c]$,
given for this problem in display \ref{eqn:defmoddom}.
The data $d$ is presumed to lie in the range space of
$S[c]$: $d \in L^2[0,T]$. It is simple to verify from the identity
\ref{eqn:defmodhom} that $S[c]$ is also surjective. That is, any data
at all can be fit by $S[c]$ with an appropriate choice of input. This
observation is important in the development of WRI, to be explained
below.

@@

This point source field depends on a function of time (``wavelet'')
$w \in L^2(\bR)$. Formally, the resulting acoustic field satisfies the
system \ref{eqn:awe1d} with $f(z,t)=w(t)\delta(z-z_s)$. Inserting this
expression in the explicit expression \ref{eqn:defmodhom}, obtain
\begin{eqnarray}
  f(z,t) & = & w(t)\delta(z-z_s),\nonumber\\
  (S[c]f)(t) &=& \frac{1}{2c}w\left(t -
                              \frac{|z_r-z_s|}{c}\right)\nonumber\\
  &= &(S_p[c]w)(t).
  \label{eqn:defmodpt}
\end{eqnarray}
$S_p[c]$ is a bounded operator with domain $L^2(\bR)$ and range
$L^2([0,T])$.

For this restricted class of source fields, the FWI problem
\ref{eqn:deffwi} can be redefined as minimization of the objective
\begin{equation}
  \label{eqn:deffwipt}
  J_{\rm FWI}[c;d,w] = \frac{1}{2}\|S_p[c]w -d\|^2.
\end{equation}
over $c$, with $d$ and $w$ treated as parameters.

To end this section, it is necessary to address an irritating
technical point: the point source defined above is not a member of the
domain of $S[c]$, as it was defined in display \ref{eqn:defmoddom}, so
the left-hand side of equation \ref{eqn:defmodpt} does not actually
make sense. The fix for this incompatibility actually elucidates the
relation between $S[c]$ and $S_p[c]$. Appendix B describes the
construction of a family of bounded injective operators  $E[c]: L^2(\bR) \rightarrow L^2([z_{\rm min},z_{\rm max}] \times \bR)$ for which
\begin{equation}
  \label{eqn:ext}
  S_p[c] = S[c] \circ E[c].
\end{equation}
This relation exhibits $S[c]$ as an {\em extension} of $S_p[c]$ as
described by \cite{Symes:09}. WRI for 1D acoustic transmission is
based on $S[c]$, and so is identified as an extended version of FWI.

@@

Note that $\alpha^2$ must have the same units as $S[c]S[c]^T$ (or
$S[c]^TS[c]$), hence {\em $W_{\alpha}[c]$ is dimensionless}. Of course
this also follows from the definition of
$ J_{\rm WRI}^{\alpha}$, which must have the same units as $J_{\rm FWI}$.

To end this discussion, it must stipulated that in any penalty method,
control of the penalty parameter has a large influence on the speed of
convergence. \cite{Aghamiry:19} use an augmented Lagrangian algorithm
to minimize the influence of the penalty weight choice. Alternatively,
one can use a version of the Discrepancy Principle to adjust $\alpha$
dynamically \cite[]{FuSymes2017discrepancy}, as the WRI problem has
the necessary features described in that paper. Since the properties
of WRI to be established in the next section are actually independent
of $\alpha>0$, I leave the matter of $\alpha$ control at that.
